Language-Based Security for Low-Level MPC

### 2024-09-08 ppdp24/slides.tex
checkpoint

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperproperties} (e.g., noninterference).
  \item Semi-automated proof techniques.
    \begin{itemize}
    \item Automatically verify small program components, manually combine for whole-program proofs. 
    \end{itemize}
  \end{itemize}

@@

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$
  \end{itemize}
  The output may leak secret information to an \cemph{adversary} trying to
  guess secret values.

@@

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt \emph{any} subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \item adversary cannot break the rules of the protol\footnote{Malicious security also
  considered separately in our work.}.
  \end{itemize}

@@

  \begin{exampleblock}{Example: 3-Party $\fplus$ in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal joint probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

\section{Example: Shamir Addition}
\begin{frame}{Example: Shamir Addition}

  To implement 3-party summation in any $\mathbb{F}_p$, we can use \emph{Shamir addition}.
  Each party first generates \emph{reconstructive shares}.

>>>>

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security model as \cemph{hyperproperties} (e.g., noninterference).
  \item Semi-automated proof techniques.
    \begin{itemize}
    \item Automatically verify small program components, manually combine for whole-program proofs. 
    \end{itemize}
  \end{itemize}

@@

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$
  \end{itemize}
  \cemph{The output may leak secret information to an adversary} trying to
  guess secret values.

@@

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt \emph{any} subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \item adversary cannot break the rules of the protocol\footnote{Malicious security also
  considered separately in our work.}.
  \end{itemize}

@@

  \begin{exampleblock}{Example: 3-Party $\fplus$} %in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal joint probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

\section{Example: Additive Sharing}
\begin{frame}{Example: Additive Secret Shares}

  To implement 3-party summation in any $\mathbb{F}_p$, we can use \emph{additive sharing}.
  Each party first generates \emph{reconstructive shares}.
